%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage{multicol}
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{}
\usepackage[hyperref]{}
\usepackage[scale=0.9]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Rounak} % Your first name
\familyname{Vyas} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum Vitae}
\address{6-3-609/10/3, Anand Nagar Colony}{Hyderabad, Telangana, India,500004}
\mobile{+91 9908550314}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{rounakvyas@outlook.com}

%----------------------------------------------------------------------------------------

\begin{document}


\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\textbf{Website}: \href{https://rounakvyas.me}{https://rounakvyas.me} \\*
\textbf{GitHub}: \href{https://github.com/itsron717}{itsron717} \\*
\textbf{LinkedIn}: \href{https://www.linkedin.com/in/itsron143/}{itsron143} 


\section{Education}

\cventry{June 2016 - July 2020}{Bachelor of Technology (B.Tech)}{Information Technology, SRM Institute of Science and Technology}{Chennai, India}{}{Undergraduate Thesis: Classification and Localisation of acne lesions using Object Detection Algorithms.\newline CGPA: 9.29/10.00}
%\cventry{2016}{D.A.V. Public School, Bistupur}{\newline Mathematics and Computer Science}{Class 12}{}{GPA -- 94.00\%}  % 
%\cventry{2014}{A.D.L.S. Sunshine School, Sakchi}{\newline Mathematics and Computer Science}{Class 10}{}{GPA -- 95.20\%}  %
%\section{%Masters Thesis}

%\cvitem{Title}{\emph{Money Is The Root Of All Evil -- Or Is It?}}
%\cvitem{Supervisors}{Professor James Smith \& Associate Professor Jane Smith}
%\cvitem{Description}{This thesis explored the idea that money has been the cause of untold anguish and suffering in the world. I found that it has, in fact, not.}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}
\cventry{Jan. 2020 - July. 2020}{Research Intern}{\httplink[Harvard Medical School]{cetbwh.org}}{Cambridge, Massachusetts}{}
{
\begin{itemize}
    \item Worked under Dr Shiladitya Sengupta at Center of Engineered Therapeutics, on Object Detection Algorithms such as Faster-RCNN and RetinaNet for localisation and classification of acne lesions. 
\end{itemize}
}

%------------------------------------------------

\cventry{Dec. 2018 - Jan. 2019}{Software Technology Intern}{\httplink[Thomson Reuters]{thomsonreuters.com/en.html}}{Hyderabad, India}{}
{
\begin{itemize}
    \item Worked in a team of 3 interns to implement a Proof of Concept to integrate ELK (Elasticsearch, Logstash, Kibana) Stack to an existing chatbot for real-time log aggregation, analysis and querying.
    \item Designed and implemented software to improve indexing time of documents by 85\% with the help of concurrency.
\end{itemize}
}

%------------------------------------------------

\cventry{June. 2018 - July. 2018}{Software Development Intern}{\httplink[OpenGenus Foundation]{opengenus.org/}}{Remote}{}{
\begin{itemize}
    \item Added tags feature with a real-time search filter to code search engine, \href{https://tinyurl.com/itsron717Contrib}{cosmos-search}. Developed a news section which uses the News API to fetch the top headlines from various sources.
    \item Created a mechanism for users to upload their markdown files which are automatically rendered on the website and also show those files during the general search.
\end{itemize}
}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Programming Skills}
%\setlength{\hintscolumnwidth}{4.2cm} % Uncomment to change the width of the dates column

\textbf{Languages}: Python, C/C++, Java \quad
\textbf{Frameworks}: Django, Flask, Keras, OpenCV \\*
\textbf{Databases}: Elasticsearch, Oracle \quad
\textbf{Work Flow}: Git, GitHub, Travis CI 
%\cvitem{Programming Languages:}{Python, C/C++, Java, JavaScript}
%\cvitem{Frameworks:}{Django, Flask, Keras, OpenCv}
%\cvitem{Databases:}{Elasticsearch, Oracle}
%\cvitem{Work Flow:}{Git, GitHub, Travis CI}
% \cvitem{Fabrication Techniques:}{Lathe, Milling, Welding, Carpentry, Soldering}

\setlength{\hintscolumnwidth}{2cm} % Uncomment to change the width of the dates column

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{Projects}
\begin{itemize}
    \item \textbf{\href{https://github.com/itsron717/XY-Calibration-3D-Printer}{calibCV}}: An automatic XY calibration system for Aether 3D-Bioprinter using Computer Vision. A web app to calculate XY offsets of multiple extruders of a 3D Bio-Printer. The project was under the supervision of \href{https://connects.catalyst.harvard.edu/Profiles/display/Person/167101}{Dr. Vivian Lee}, Harvard Medical School.
    \item \textbf{\href{https://github.com/itsron717/markov-gen}{markov-gen}}: A Markov Chain Text Generator used to randomly generate (somewhat) realistic sentences, using words from a source text. Words are joined together in sequence, with each new word being selected based on how often it follows the previous word in the source document.
    \item \textbf{\href{https://github.com/itsron717/es-indexer}{es-indexer}}: A \href{https://pypi.org/project/es-indexer/0.1/}{PyPi package} to populate json data into elasticsearch efficiently using multi-threading. 
\end{itemize}






%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards and Extracurriculars}

\cvitem{Aug. 2019}{Speaker, \href{https://python.nz/kiwipycon.talk.rounakvyas}{PyCon New Zealand} (Kiwi PyCon X), Scholarship: 500 NZD ($\approx$ Rs. 23000).}
\cvitem{Mar. 2019}{3\textsuperscript{rd} Place, Ctrl-Alt-Code IoT Hackathon. Team Captain: Team \textit{Park.ai}.}
\cvitem{Jan. 2019}{Finalist, Microsoft MSHack Hackathon. Team Captain: Team \textit{Dr.Phil}.}
\cvitem{Jun. 2018}{Academic Scholarship of Rs. 21500, Department Rank Holder List, 2017-2018.}
\cvitem{Aug. 2017}{Student Researcher, Artificial Intelligence, {\httplink[Next Tech Lab]{nextech.io/}}{}, Chennai, India.}
\cvitem{Jan. 2012}{Table Tennis: Top 8 of 100+ teams in  School Games Federation of India Nationals.}

\end{document}

